Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-25 proposal/prop.tex
prop

@@

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value} \footnote{Need to verify whether this example is convex or not.}Given
a three dimensional Hilbert space with an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{ }$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$, $\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$,
and a quantum $\mathscr{I}$-interval-valued probability measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$
defined as follow, where the state vectors corresponding to 1-dimensional
projector are also illustrated in figure~\ref{fig:three-dimensional-4-value}.
\begin{enumerate}
\item Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
\end{eqnarray*}
 where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
dotted vector, respectively.
\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
\end{enumerate}
That $\bar{\mu}$ has an empty core can be proved by contradiction.
Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]

@@

\footnote{This example is a little bit too long to human-verify, and
we need more examples. Maybe we need to write a program for further
verification.}

@@

Born
KS: Mermin-Meyer

@@

>>>>

This is the most developed part of our current investigation and is
more detailed.

@@

\begin{example}[Three-dimensional quantum 4-value interval-valued
probability measure]\label{ex:three-dimensional-4-value} 
Question: Is this convex? Given a three dimensional Hilbert space with
an orthonormal basis $\left\{ \ket{0},\ket{1},\ket{2}\right\} $.
Consider\emph{
}$\mathscr{I}=\left\{ \imposs,\unlikely,\likely,\necess\right\} $,
$\ket{\ps}=\frac{1}{\sqrt{2}}(\ket{0}+\ket{1})$,
$\ket{\ms}=\frac{1}{\sqrt{2}}(\ket{0}-\ket{1})$, and a quantum
$\mathscr{I}$-interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ defined as follow,
where the state vectors corresponding to 1-dimensional projector are
also illustrated in figure~\ref{fig:three-dimensional-4-value}.
\begin{enumerate}
\item Let 
\begin{eqnarray*}
\bar{\mu}(\mathbb{0})=\bar{\mu}(\proj{0})=\bar{\mu}(\proj{\ps}) & = & \imposs\\
\bar{\mu}(\mathbb{1})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0})=\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps}) & = & \necess\textrm{ ,}
\end{eqnarray*}
 where $\ket{0}$ and $\ket{\ps}$ is illustrated as the red and green
dotted vector, respectively.
\item Consider the red and green circles in figure~\ref{fig:three-dimensional-4-value}.
They are the states orthogonal to $\ket{0}$ and $\ket{\ps}$, respectively,
and can be parametrized as $\ket{0_{\theta,\gamma}^{\perp}}=\rme^{\rmi\gamma}\sin\theta\ket{1}+\cos\theta\ket{2}$
and $\ket{\ps_{\theta,\gamma}^{\perp}}=-\rme^{\rmi\gamma}\sin\theta\ket{\ms}+\cos\theta\ket{2}$,
where $0\le\theta\le\frac{\pi}{2}$ and $0\le\gamma<2\pi$. The dotted
half of those states need special treatment, i.e., whenever $0\le\theta<\frac{\pi}{2}$
and $0\le\gamma<\pi$, we define 
\begin{eqnarray*}
\bar{\mu}\left(\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \likely\\
\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{0_{\theta,\gamma}^{\perp}}\right)=\bar{\mu}\left(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\ps_{\theta,\gamma}^{\perp}}\right) & = & \unlikely\textrm{ .}
\end{eqnarray*}
\item Otherwise, $\bar{\mu}(\proj{\psi})=\unlikely$ and $\bar{\mu}(\mathbb{1}\tensor*[_{\mathscr{O}}]{-}{}\proj{\psi})=\likely$. 
\end{enumerate}
That $\bar{\mu}$ has an empty core can be proved by contradiction.
Assume there is a real-valued probability measure satisfying $\mu_{\rho}^{B}(P)\in\bar{\mu}(P)$
for all $P\in\events$. Because $\mu_{\rho}^{B}(\proj{0})\in\bar{\mu}(\proj{0})=\imposs$
and $\mu_{\rho}^{B}(\proj{\ps})\in\bar{\mu}(\proj{\ps})=\imposs$,
we must have $\mu_{\rho}^{B}(\proj{0})=\mu_{\rho}^{B}(\proj{\ps})=0$
so that $\mu_{\rho}^{B}=\mu_{\ket{2}}^{B}$. However, 
\[
\mu_{\ket{2}}^{B}(\proj{2})=1\notin\unlikely=\bar{\mu}(\proj{2})\textrm{ .}
\]

@@

@@

Given quantum state as interactive system
and interval-valued probability
and perhaps additionally discrete states in finite fields (try with or without)
investigate gleason (born), bell, KS, and revisit Mermin-Meyer and
other debates and paradoxes

@@

If power of observer is limited with respect to power of quantum state
then quantum state can always ``fool'' you and get away with things;
you don't have the resources to catch it in an inconsistent state; if
state is interactive and always ``uncommitted'' until you make your
move you can never catch it in a lie

explain secret key exchange; if attacker has limited power cannot
crack it; complexity crucial.
